An Overview of the Current State of the Test-First vs. Test-Last Debate

### 2013-11-27 Paper_Draft.tex
Corrected a quick issue in the paper.

In 2007 an opinion study was conducted by Janzen \cite{Janzen:2007}.  In this opinion study, Janzen polled participants from six experiments to determine whether they preferred testing with test-first methods or test-last methods.  Five of these experiments were conducted on students at the University of Kansas while one of the experiments was conducted on professional programmers from a Fortune 500 company.   Each participant was asked six questions where they had to choose between test-first and test-last testing.  The questions were:

@@

One of the studies that Hammond et al summarizes is the opinion study by Janzen.  In particular Hammond focuses on a quote from Janzens study: ``A few of the participants of the studies found TDD either too difficult or too different from what they normally do''.  This quote refers to an interesting relation found between the choice and best approach category.  It was noted by Janzen that in every experiment, there were more people who thought test-first was the best approach than people who would choose to implement test-first testing.  When Janzen looked into why this phenomena had occurred he found multiple statements in the comment section that claimed the difficulties of TDD.

@@

\subsection{Discussion}
The data above shows fairly strong evidence that TDD is at least somewhat difficult to implement but none of the data above shows that test-first testing is the problem.  In the first study, Janzen reveals that TDD was difficult for some people to implement.  In the second study, George and Williams reveal that 56\% of the participants found the TDD mindset hard to adapt while only 23\% of the participants found testing before designing as a problem, suggesting that something other then test-first testing caused difficulty for at least 33\% of the participants.  The third study showed that programmers had trouble implementing the steps of TDD, which has nothing to do with testing before designing.  With these studies in mind, difficulty in using TDD does not seem to be directly linked with test-first testing.

>>>>

In 2007 an opinion study was conducted by Janzen \cite{Janzen:2007}.  In this opinion study, Janzen polled participants from six TDD experiments to determine whether they preferred testing with test-first methods or test-last methods.  Five of these experiments were conducted on students at the University of Kansas while one of the experiments was conducted on professional programmers from a Fortune 500 company.   Each participant was asked six questions where they had to choose between test-first and test-last testing.  The questions were:

@@

One of the studies that Hammond et al summarizes is the opinion study by Janzen.  In particular Hammond focuses on a quote from Janzens study: ``They found that while some programmers saw the benefits of the test-first approach, several of the programmers had the perception that it was too difficult or too different from what they normally do''.  This quote refers to an interesting relation found between the choice and best approach category.  It was noted by Janzen that in every experiment, there were more people who thought test-first was the best approach than people who would choose to implement test-first testing.  When Janzen looked into why this phenomena had occurred he found multiple statements in the comment section that claimed the difficulties of implementing test-first methods (which in this study was TDD).

@@

\subsection{Discussion}
The data above shows fairly strong evidence that TDD is at least somewhat difficult to implement but none of the data above shows that test-first testing is the problem.  In the first study, Janzen reveals that test-first methods, in the form of TDD, were difficult for some people to implement.  In the second study, George and Williams reveal that 56\% of the participants found the TDD mindset hard to adapt while only 23\% of the participants found testing before designing as a problem, suggesting that something other then test-first testing caused difficulty for at least 33\% of the participants.  The third study showed that programmers had trouble implementing the steps of TDD, which has nothing to do with testing before designing.  With these studies in mind, difficulty in using TDD does not seem to be directly linked with test-first testing.
